Comb associative operads

### 2018-08-28 CAs_operads.tex
Lemme 3.2.6

>>>>

\Todo{Christophe : je vous propose cette démo}
\begin{proof}
    We consider the rewrite rule $\LComb{\gamma} \Rew \RComb{\gamma}$ 
    on $\Mag$. First, we show that 
    \begin{equation} \label{eq:rewriting_invariant}
        \Tfr \RewContext \Tfr' 
        \mbox{ implies that }
        \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right) 
        \, \pmod{\bar{\gamma}}.
    \end{equation}
    Indeed for all $\Tfr \in \Mag$, there exist binary trees 
    $\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)}$ such that
    \begin{math}
      \Tfr = 
      \left[\, |,\Tfr_1, \dots, \Tfr_{\LRank\left(\Tfr\right)} \right].
    \end{math}
    Thus if $\Tfr \RewContext \Tfr'$, then one of the 
    two following cases occurs :
    \begin{enumerate}[label={(\it\roman*)}]
        \item there exist $\Tfr_i'$ such that
            \begin{math}
              \Tfr' = \LComb{\LRank\left(\Tfr\right)} \circ 
              \left[\, | ,\Tfr_1, \dots, \Tfr_i',\dots, 
                    \Tfr_{\LRank\left(\Tfr\right)}
              \right] \mbox{ so } 
              \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right);
            \end{math}
        \item there exist $i$ such that
            \begin{math} 
              \Tfr' = \LComb{\LRank\left(\Tfr\right)-\bar{\gamma}} \circ
              \left[ | ,\Tfr_1, \dots, 
                 \RComb{\bar{\gamma}} \circ 
                 [\Tfr_{i},\dots, \Tfr_{i+\bar{\gamma}}]
                 ,\dots, \Tfr_{\LRank\left(\Tfr\right)}
              \right]\\
              \mbox{ so }
              \LRank\left(\Tfr'\right) = 
              \LRank\left(\Tfr\right) - \bar{\gamma} = 
              \LRank\left(\Tfr\right) \pmod{\bar{\gamma}}
            \end{math}.
    \end{enumerate} 
    This concludes the proof of~\ref{eq:rewriting_invariant}.  
    \smallbreak

    We deduce from~\ref{eq:rewriting_invariant} that the equivalence 
    relation $r$ defined by 
    \begin{equation}
        r(\Tfr, \Tfr') \mbox{ if and only if } 
        \LRank\left(\Tfr'\right) = \LRank\left(\Tfr\right) 
        \, \pmod{\bar{\gamma}}
    \end{equation}
    contains the relation $\RewContext$ and thus its transitive 
    and symmetric closure, which is $\CongrCAs{\gamma}$.
\end{proof}
